%-------------------------------------------------------%
%                         英文摘要
%-------------------------------------------------------%
\chapter*{\textbf{ABSTRACT}}
\eabstractpagestyle % 中文摘要的页眉页脚

In order to further standardize the format of dissertation/thesis writing and improve graduate dissertation/thesis quality, this specification is formulated with reference to the national standard "Presentation of academic papers" (GB/T 7713.2-2022) and the reality of SWJTU.

The main changes in this revision from the last version are as follows.

1. Rewrite the document according to the requirements of the specifications, and preset main formatting styles, which can be used as a template directly.

2. Update the writing instructions of abstract, introduction, main chapters, and conclusions, as well as the notes on language and presentation.

3. Adjust the format requirements of references according to the latest national standards.

4. Clarify some details of format requirements, e.g., three-line style for tables, format for figure/table annotations, the problem of cross page figure/table.

5. Add comparison tables of Chinese and English names of colleges, academic degree disciplines, and professional degree categories in Appendixes.

This document can be downloaded from the Graduate School website. In case of any changes, the latest version published on the Graduate School website shall prevail.

\vspace{1em}

\noindent \hangindent=4.9em \textbf{Keywords: }Dissertation/Thesis, Writing Format, Main Changes